\documentclass[12pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\usepackage{microtype}
\usepackage{times}
\usepackage{longtable}

\begin{document}

\begin{center}
\textbf{Consolidated Claim Document – Prolongation and Supplementary Heads}\\
Contract Package: ARTL/WIPL/2021/001\\
Period: 1 Sep 2023 – 30 Jun 2025 (22 months)\\
Submission Date: \today
\end{center}

\section*{1. Executive Summary}
\begin{itemize}
  \item Total Combined Claim Context (per DESPATCH): \textbf{INR 630.96 Crores}.
  \item Interim Relief Requested: \textbf{INR 250.00 Crores} on-account, adjustable.
  \item Basis: Employer-attributable delays (RoW, utilities, design/variations, approvals) impacting critical path; notices served within time.
\end{itemize}

\section*{2. Contractual Basis}
\begin{longtable}{p{0.35\textwidth}p{0.6\textwidth}}
Site Possession/ROW & Clause 2.1 / [Concession Clause __] \\
Extension of Time (EOT) & Clause 8.4 \\
Prolongation Compensation & Clause 8.5 \\
Variations/Change of Scope & Clause 13.1 \\
Claims Procedure/Time Limits & Clause 20.1 \\
Performance Securities & Clause 4.2 \\
Payment Terms/Interest & Clause 11.1 \\
\end{longtable}

\section*{3. Claim Heads and Quantum}
\begin{longtable}{p{0.52\textwidth}p{0.18\textwidth}p{0.25\textwidth}}
\textbf{Head} & \textbf{Amount (INR Cr)} & \textbf{Appendix} \\
\hline
Disruption/Productivity Loss (Measured Mile) & 62.00 & H \\
Constructive Acceleration Costs & 25.00 & I \\
Extended Bonds/Guarantees/Insurances & 9.15 & J \\
Environmental and Regulatory Compliance & 11.00 & K \\
Subcontractor Standby (Pass-Through) & 20.00 & L \\
Variations/Change of Scope (Direct + Time) & 35.00 & M \\
Interest on Delayed Payments (separate) & 5.23 & N \\
Loss of Opportunity (Alternative) & 40.00 & O \\
\textbf{Subtotal – Supplementary Primary (1–6)} & \textbf{162.15} & \\
\end{longtable}

\section*{4. Causation and Anti–Double Counting}
Each head is mapped to specific delay causes and periods. Overlap with time-related prolongation heads is excluded; variation direct costs are segregated from prolongation. Interest on delayed payments is separate from financing costs.

\section*{5. Evidence and Annexures}
\begin{itemize}
  \item Appendix H: Measured-mile logs, MPRs, hindrance/Section open logs.
  \item Appendix I: Acceleration notices/approvals, shift rosters, plant logs.
  \item Appendix J: Bond/guarantee extensions, insurance endorsements, invoices.
  \item Appendix K: Environmental permits/renewals, monitoring invoices, liaison records.
  \item Appendix L: Subcontractor standby certifications, invoices, correspondence.
  \item Appendix M: Variation orders, computations, delay impact notes, Engineer certifications.
  \item Appendix N: IPC/payment schedules, bank statements (interest computation).
  \item Appendix O: Bid logs, capacity statements (alternative claim support).
\end{itemize}

\section*{6. Prayer for Relief}
\begin{enumerate}
  \item Determine and pay INR 162.15 Crores under Heads H–M.
  \item Pay interest on delayed payments of INR 5.23 Crores subject to reconciliation.
  \item Consider Loss of Opportunity (INR 40.00 Crores) as an \emph{alternative} claim where appropriate.
  \item Grant interim on-account payment of INR 250.00 Crores pending final determination.
  \item Reserve Contractor's rights to update computations and seek ongoing costs beyond 30 Jun 2025.
\end{enumerate}

\end{document}


