\documentclass[12pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\usepackage{microtype}
\usepackage{times}

\begin{document}
	

	
	% Subject
	\textbf{Subject}: Claim for Compensation Arising from Employer-Attributable Delays and Disruptions -- Prolongation Costs from 1 September 2023 to 30 June 2025
	
	% Salutation
	Dear Sir/Madam,
	
	% Body
	\begin{enumerate}
		\item We refer to our previous correspondence, including our Extension of Time (EOT) claim submitted vide letter no. 2134 dated 7 July 2025, and our letter dated [insert date] regarding the Supplementary Agreement executed on 12 March 2024. By this letter, we formally submit our claim for compensation under Contract Package ARTL/WIPL/2021/001 for additional costs and losses incurred due to delays and disruptions attributable to the Employer, from the Contract’s inception through 30 June 2025.
		\item As detailed in our EOT submission, the principal causes of delay include:
		\begin{itemize}
			\item Failure to provide timely access to the Site and Right of Way (RoW) as required under Clause [e.g., 2.1] of the Concession Agreement and Clause [e.g., 4.7] of the Contract.
			\item Delays in tree removal and utility relocation.
			\item Repeated piecemeal changes to the Scope of Works, including introduction of unforeseen major structures.
			\item Delays in approving Change of Scope Works under Clause [e.g., 13.1].
		\end{itemize}
		\item These events, which are Employer risks under the Contract, have been substantiated with contemporaneous records in our EOT claim. At the original completion date (August 2023), approximately 58\% of the Main Carriageway (MCW) and 46\% of the Service Road (SR) remained unavailable. Even by 31 January 2025, 25\% of the MCW was still not handed over. Execution in available sections was further hindered by utility and design delays.
		\item Pursuant to Clauses [e.g., 8.4 (EOT), 8.5 (Prolongation Costs), and 20.1 (Claims)] of the Contract, we are entitled to compensation for all direct and foreseeable consequences of these delays.
		\item The Contractor has incurred disruption costs due to fragmented and stop--start execution caused by piecemeal site handovers, utility delays, and late approvals. These inefficiencies, distinct from prolongation, resulted in reduced productivity and additional expenditure, estimated at \texttt{INR 62 Crores}, as detailed in Appendix H of the enclosed Claim Evaluation Note.
		\item We further submit a claim for acceleration costs, necessitated by the Employer’s delays and lack of timely EOT relief. To mitigate exposure to liquidated damages and maintain progress, the Contractor implemented overtime, additional plant deployment, and compressed schedules, incurring costs estimated between \texttt{INR 15--35 Crores}. Supporting records are provided in Appendix I.
		\item Additionally, we include a claim for extended bond, insurance, and guarantee costs, arising from the prolonged project duration due to Employer defaults. Extensions of performance bonds, advance payment guarantees, and project insurance policies (Contract Works, Third-Party Liability) resulted in costs estimated between \texttt{INR 6--12 Crores}, supported by renewal certificates and invoices in Appendix J.
		\item We also submit a claim for escalation beyond Contract provisions, covering increased costs for materials such as cement and steel due to prolonged execution, estimated at \texttt{INR 15 Crores}, as detailed in Appendix K of the Claim Evaluation Note.
		\item We further submit a claim for environmental and regulatory compliance costs, incurred due to extended obligations for borrow area permits, environmental monitoring, and MoEFCC reporting. These unforeseen costs, estimated between \texttt{INR 7--18 Crores}, are supported by regulatory correspondence and payment records in Appendix K.
		\item We also claim idle time and standby costs for subcontractors, arising from fragmented site availability due to Employer delays. Subcontractors, mobilized per approved schedules, incurred standby costs estimated between \texttt{INR 12--25 Crores}, supported by invoices and correspondence in Appendix L.
		\item Additionally, we claim for variations and change of scope, driven by Employer-instructed modifications, such as new structures and piecemeal scope changes. These caused direct costs and prolongation impacts, valued between \texttt{INR 25--60 Crores}, as detailed in Appendix M.
		\item We further include a claim for interest on delayed payments, separate from financing costs, due to the Employer’s failure to release certified amounts within stipulated timeframes. This financial loss, estimated between \texttt{INR 12--18 Crores}, is supported by schedules and bank statements in Appendix N. This claim is merged with head H to avoid overlap.
		\item Finally, we record a claim for consequential losses, arising from Employer-caused prolongation that prevented pursuit of other projects. These foreseeable losses, estimated between \texttt{INR 10--20 Crores}, are recoverable under Section 73 of the Indian Contract Act, 1872, subject to contractual allowances, and are merged with head F. Supporting evidence is provided in Appendix O.
		\item The original 22-month Contract has now extended beyond 46 months, with completion potentially requiring at least 12 additional months if remaining hindrances are removed. These unforeseen delays have strained our cash flow, necessitating external financing despite mitigation efforts (e.g., partial resource redeployment).
		\item To maintain project progress and avoid further disruptions, we request interim relief of \texttt{INR 250 Crores} under Clause [e.g., 14.8 (Advance Payment)] or as an on-account payment, representing approximately 40\% of the total claimed amount of \texttt{INR 630.96 Crores}. This can be adjusted against the final determined sum following review and discussion.
		\item We invite prompt discussions to resolve this claim amicably and request your response within [e.g., 14 days]. We reserve all rights under the Contract, including to update this claim with further evidence or costs.
	\end{enumerate}
	
	% Closing
	Yours faithfully, \\
	\vspace{1cm} \\
	Authorized Signatory \\

	
	% Enclosures and cc
	Enclosures: Claim Evaluation Note (Supplementary Claims 8--16, with Appendices H--O) \\
	cc: ARTL HQ, Ahmedabad; Office Copy.
	
\end{document}