\documentclass[12pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\usepackage{microtype}
\usepackage{times}

\begin{document}

\textbf{Subject}: Submission of Consolidated Claim with Supplementary Heads – Employer-Attributable Delays (1 Sep 2023 to 30 Jun 2025)

Dear Sir/Madam,

\begin{enumerate}
  \item We hereby submit our consolidated claim package under Contract Package ARTL/WIPL/2021/001, covering prolongation and supplementary claim heads arising from Employer-attributable delays and disruptions during the period 1 September 2023 to 30 June 2025.
  \item Principal delay causes include delayed Right of Way (RoW) handover, utility shifting and tree removal delays, design/variation approval delays, and administrative approvals, each impacting the critical path. Notices and contemporaneous records have been maintained and previously shared with the Engineer.
  \item The consolidated quantum, including supplementary heads and interest context per DESPATCH drafts, is \texttt{INR 630.96 Crores}. In order to maintain progress and mitigate further cost escalation, we request an interim on-account payment of \texttt{INR 250.00 Crores}, adjustable against the final determination.
  \item The package includes additional claim heads distinct from prolongation: Disruption/Productivity Loss (Appendix H), Constructive Acceleration (Appendix I), Extended Bonds/Guarantees/Insurances (Appendix J), Environmental Compliance (Appendix K), Subcontractor Standby (Appendix L), and Variations/Change of Scope (Appendix M). Interest on delayed payments is presented separately (Appendix N) to avoid overlap with financing costs. Loss of Opportunity is preserved as an alternate claim (Appendix O).
  \item We confirm that double counting is expressly avoided. Overlaps with time-related plant/labour/overhead heads are excluded; variation-linked direct costs are separated from prolongation costs; and interest on delayed payments is segregated from general financing costs.
  \item We propose a technical meeting within 14 days for joint review of computations and supporting evidence. Upon agreement on methodology, we request certification of undisputed amounts and release of interim payment.
  \item This submission is without prejudice to our rights under the Contract and applicable law, including the right to update computations and seek additional compensation for ongoing delays beyond 30 June 2025.
\end{enumerate}

Yours faithfully,\\[10pt]
Authorised Signatory\\
Wagad Infraprojects Private Limited

\vspace{10pt}
\textbf{Enclosures}: Consolidated Claim Document (with Annexures A–O); Evidence Package; Excel Computation Workbook (Supplementary\_Claims\_Template.xlsx)

\end{document}


